\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-06-28 manuscript/manuscript.tex
updated figure

		% Keywords
		\noindent {\textbf{Keywords}\\
			clustering, neural network, transcriptomics, chemotherapeutic response, combinatorial biomarker, molecular profile, therapeutic sensitivity, cancer}
	\end{abstract} \vspace{1em}
]

@@

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden-\m) at (1.25,-1.75-\y) {\foo{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden1-\m) at (2.5,-1.75-\y) {\hehe{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden2-\m) at (3.75,-1.75-\y) {\hehetwo{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden3-\m) at (5,-1.75-\y) {\hehethree{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
			\node [every neuron/.try, neuron \m/.try] (hidden4-\m) at (6.25,-1.75-\y) {\hehefour{\l}};

        \foreach \m/\l [count=\y] in {1}
            \node [every neuron/.try, neuron \m/.try] (output-\m) at (7.5,0-2.5-\y) {$O_1$};

        % arrows
        \foreach \l [count=\i] in {1,2,3,4,5,300}
            \draw [<-] (input-\l) -- ++(-1,0) node [above, midway] {};

@@

        \foreach \l [count=\i] in {1}
            \draw [->] (output-\l) -- ++(+1,0) node [above, midway] {};

        % labelling layers
        \foreach \l [count=\x from 0] in {Input\\layer, Hidden\\layer 1, Hidden\\layer 2, Hidden\\layer 3, Hidden\\layer 4, Hidden\\layer 5, Output\\layer}
            \node [align=left, above] at (\x*1.25, -0.5) {\l};

>>>>

		% Keywords
		\noindent {\textbf{Keywords}\\
			clustering, neural network, transcriptomics, chemotherapeuticbdc response, combinatorial biomarker, molecular profile, therapeutic sensitivity, cancer}
	\end{abstract} \vspace{1em}
]

@@

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden-\m) at (1.5,-1.75-\y) {\foo{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden1-\m) at (3,-1.75-\y) {\hehe{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden2-\m) at (4.5,-1.75-\y) {\hehetwo{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
            \node [every neuron/.try, neuron \m/.try] (hidden3-\m) at (6,-1.75-\y) {\hehethree{\l}};

        \foreach \m/\l [count=\y] in {1,missing,100}
			\node [every neuron/.try, neuron \m/.try] (hidden4-\m) at (7.5,-1.75-\y) {\hehefour{\l}};

        \foreach \m/\l [count=\y] in {1}
            \node [every neuron/.try, neuron \m/.try] (output-\m) at (9,0-2.5-\y) {$O_1$};

        % arrows

@@

        % labelling layers
        \foreach \l [count=\x from 0] in {Input\\layer, Hidden\\layer 1, Hidden\\layer 2, Hidden\\layer 3, Hidden\\layer 4, Hidden\\layer 5, Output\\layer}
            \node [align=left, above] at (\x*1.5, -0.5) {\l};
